### 2015-07-12 narrative/naming-service.tex
finishing up naming service.

While pure object stores, such as those popular in the big data
domain~\cite{Fitzpatrick:2004:memcached}, others avoid this bottleneck by
strictly offering an object ID with the application required to manage how this
ID maps to something of interest. This approach of removing the metadata
service from the system level completely can work well for scale out
applications where data is created or consumed by a single process at a time or
just in a work queue rather than potentially O(1 million) processes all
actively collectively for a single ``object''. To address this case, having
some system integrated metadata services to associate names with these object
is a preferable solution. While it will not have the same synchronous
consistency semantics as POSIX, we will offer something as close as possible to
address legacy application and command-line style data access and migration to
other storage types using these POSIX semantics.

\paragraph{Challenge:}
The main challenge of incorporating the additional, rich metadata will be
joined by the additional challenge of coordinating with the other storage and
application-layer services to offer the best access times possible for data
stored in the system. The developed metadata services that drive data
compression and subsetting operations must have easy, consistent, and ideally
non-blocking or locking access to this metadata service. We must investigate
how to build such a metadata and naming service that also incorporates and
maintains the additional metadata required to support our advanced
functionality.

Our research in this area will address the following questions:
(1) Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?, 
(2) For POSIX API requests, how do we respond if only varying data fidelity
  levels are available for the requested data object?, 
(3) What level of metadata should we maintain and keep in sync to enhance
  response quality within time-bound requests?, 
(4) How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?, and
(5) How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?

>>>>

In pure object stores, such as those popular in the big data
domain~\cite{Fitzpatrick:2004:memcached}, one avoids this bottleneck by
strictly offering an object ID with the application required to manage how this
ID maps to something of interest. This approach of removing the metadata
service from the system level completely can work well for scaling out
applications where data is created or consumed by a single process at a time or
just in a work queue, rather than potentially O(1 million) processes all
actively requesting for a single ``object''. To address this case, having
some system integrated metadata services to associate names with these object
is a preferable solution. We will offer solutions to
address legacy application and command-line style data access and migration to
other storage types using these POSIX semantics, without providing the same synchronous
consistency semantics as POSIX.

\paragraph{Challenge:}
The main challenge of incorporating the additional, rich metadata will be
joined by the additional challenge of coordinating with the other storage and
application layer services to offer the best access times possible for data
stored in the system. The developed metadata services that drive data
compression and subsetting operations must have easy, consistent, and ideally
non-blocking or locking access to this metadata service. We must investigate
how to build such a metadata and naming service that also incorporates and
maintains the additional metadata required to support our advanced
functionality.

Our research in this area will address the following specific questions:
(1) Since the metadata will be distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?, 
(2) For POSIX API requests, how do we respond if only varying data fidelity
  levels are available for the requested data object?, 
(3) What level of metadata should we maintain and keep in sync to enhance
  response quality within time-bound requests?, 
(4) How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?, and
(5) How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?
